Non-stationary local time-frequency transform

### 2021-03-01 tf/paper.tex
fix tf

\multiplot{4}{ppltft-new,ppltftn-new,pswltft-new,pswltftn-new}{width=0.45\textwidth}{Time-frequency spectra cubes using (a) traditional LTFT method and (b) non-stationary LTFT method for the PP image before matching, (c) traditional LTFT method and (d) non-stationary LTFT method for the warped PS image before matching.}

>>>>

\multiplot{4}{ppltft,ppltftn,pswltft,pswltftn}{width=0.45\textwidth}{Time-frequency spectra cubes using (a) traditional LTFT method and (b) non-stationary LTFT method for the PP image before matching, (c) traditional LTFT method and (d) non-stationary LTFT method for the warped PS image before matching.}
